A hierarchical model to evaluate pest treatments from prevalence and intensity data

### 2023-09-02 Article.qmd

```{r simulations, cache = TRUE, eval = TRUE, results = 'hide'}
# The following code presents the inference for one seed. As the calculus 
# time is growing fast with the number of trials and the number of sampled
# values, we set here the number of trials to 10 (I = 10) and the number
# of adaptations and iterations to 2000.

# Ours simulations results are obtained by running this code for I = 10, 20, 
# 40, 80, for all seeds between 0 and 999, with a number of adaptations and
# iterations equal to 36000. We used the Migale server from INRAE to run 
# these simulations.

# Function to simulate data ################################################
J = 4;   T = 3;   N = 10;   K = 4;

>>>>

::: {.callout-note}
The following code presents the inference for one seed. As the calculus
time is growing fast with the number of trials and the number of sampled
values, we set here the number of trials to 10 (I = 10) and the number
of adaptations and iterations to 2000.

Our simulations results are obtained by running this code for I = 10, 20,
40, 80, for all seeds between 0 and 999, with a number of adaptations and
iterations equal to 36000. We used the Migale server from INRAE to run
these simulations.
:::

```{r simulations, cache = TRUE, eval = TRUE, results = 'hide'}
J = 4;   T = 3;   N = 10;   K = 4;
